The Blue Obelisk five years on

### 2011-03-14 paper.tex
Info on ChemiSQL

One of the effects of the Blue Obelisk has been to bring developers together from different Open Source chemistry projects so that they look for opportunities to collaborate rather than compete, and to leverage work done by other projects to avoid duplication of effort.

As an example of this, when in March 2008 the Jmol development team were looking to add support for energy minimisation, rather than implement a forcefield from scratch they ported the UFF forcefield implementation from Open Babel to Jmol. This code has allowed Jmol to support 2D to 3D conversion of structures (through energy minimisation).

>>>>

One of the effects of the Blue Obelisk has been to bring developers together from different Open Source chemistry projects so that they look for opportunities to collaborate rather than compete, and to leverage work done by other projects to avoid duplication of effort. As an example of this, when in March 2008 the Jmol development team were looking to add support for energy minimisation, rather than implement a forcefield from scratch they ported the UFF forcefield implementation from Open Babel to Jmol. This code has allowed Jmol to support 2D to 3D conversion of structures (through energy minimisation).

Another collaborative initiative between Blue Obelisk projects was the establishment in May 2008 of
the ChemiSQL project. This brought together the developers of several
open source chemistry database cartridges (PgChem, MyChem, OrChem and
more recently Bingo) with a view to making their database APIs more
similar and collaborating on benchmark datasets for assessing
performance. For two of these projects, PgChem and MyChem, which are both based on
Open Babel, there is the additional possibility of working together on a shared
codebase.
